Simulation Explorer

### 2017-12-21 inst/rmd/vis_sim.Rmd
Fix hover text label for total abundance plot in vis_sim.Rmd

library(plotly)
library(viridis)
library(shiny)
e <- new.env() # make a new environment to keep the global clean
e$sim <- temp  # temp object (in global) created by vis_sim function
rm(temp)       # clean-up
e$ages <- e$sim$ages
e$years <- e$sim$years
e$vis_distribution <- "sp_N" %in% names(e$sim)

@@

```{r}
e$tot <- data.frame(Year = e$years, N = colSums(e$sim$N))
e$tot$text <- paste0("Year: ", e$tot$year, "\nN: ", round(e$tot$N))
plot_ly(x = ~Year, y = ~N, text = ~text, hoverinfo = "text",
        type = "scatter", mode = "lines", data = e$tot) %>%
  layout(xaxis = list(rangeslider = list(type = "date")))
```

>>>>

library(plotly)
library(viridis)
library(shiny)
e <- new.env() # make a new environment to keep the global clean (rmarkdown::run wants to work in the global)
e$sim <- temp  # temp object (in global) created by vis_sim function
rm(temp)       # clean-up
e$ages <- e$sim$ages
e$years <- e$sim$years
e$vis_distribution <- "sp_N" %in% names(e$sim)

@@

```{r}
e$tot <- data.frame(Year = e$years, N = colSums(e$sim$N))
e$tot$text <- paste0("Year: ", e$tot$Year, "\nN: ", round(e$tot$N))
plot_ly(x = ~Year, y = ~N, text = ~text, hoverinfo = "text",
        type = "scatter", mode = "lines", data = e$tot) %>%
  layout(xaxis = list(rangeslider = list(type = "date")))
```
